QPLIB: A Library of Quadratic Programming Instances

### 2018-02-08 QPLIB-3.tex
problem types should be formatted in italics

At the end of this process we had gathered more than eight thousand
instances. Three quarters of them contained discrete variables, while
the remainder contained only continuous variables. In more detail,
we gathered $\approx 1800$ Quadratic Binary Linear (QBL) instances,
$\approx 2000$ Quadratic Continuous Quadratic (QCQ) instances,
and $\approx 2500$ Quadratic General Quadratic (QGQ) instances. We
also received $\approx 1000$ Convex General Convex (CGC) instances. We
obtained relatively fewer Quadratic Binary Quadratic (QBQ), Convex
Continuous Convex (CCC) and Convex Mixed Convex (CMC) instances,
($\approx 150$, $\approx 200$, and $\approx 200$ instances, respectively).
Finally, we found only $17$ Quadratic Mixed
Linear (QML) instances. In the call for instances, no specific format
requirements were imposed for the submissions.

@@

During the development of the library, a discussion ensued about
the expected goals that we wished to achieve. The following four goals
were finally identified:
%
\begin{enumerate}
 \item to represent as far as possible all the different categories of QP
       problems;
 %
 \item to gather ``challenging'' instances, i.e., ones which can not be easily
       solved by  state-of-the-art solvers;
 %
 \item to include, for each of the categories, a set of well-diversified
       instances; and
 %
 \item to obtain a set of instances which is neither too small, so as to
       preserve statistical relevance, nor too large so as to being
       computationally manageable.
\end{enumerate}
%
To achieve such goals, we performed the following two filters, applied in
a cascade.
%
\begin{itemize}
 \item \emph{First Instances Filter.}\\
       The first filter was designed to drastically reduce the number of
       instances by eliminating the ``easy'' ones. An empirical measure
       for the hardness of an instance is the CPU time needed by a
       complete solver (cf.~\S\ref{sec:algo}) to solve it to
       global optimality. Accordingly, for each of the gathered instance we
       ran the complete solvers in GAMS, which number depends on the category
       of the instance under consideration, cf.~Table \ref{t:solvers}.
       We then filtered according to a first
       measure of computational difficulty, i.e., we discarded all instances
       that are solved by at least 30\% of the complete solvers within a time
       limit of 30 seconds.
 %
 \item \emph{Second Instances Filter.}\\
       The goal of the second filter was to eliminate ``similar'' instances.
       We carefully analyzed the instances one by one, and we clustered them
       according to their features; for each cluster we kept only a few
       representatives, e.g. by eliminating all but a few of those with very similar size and coming from the same donor. Finally, in order to only
       keep computationally challenging instances we ran a complete solver for QGQ with a time limit of 120 seconds; all the
       instances which have been solved to proven optimality within this time limit
       were discarded.
\end{itemize}
%
In Table~\ref{tab:filters} we summarize the two filter steps, which
allowed us to identify the final set of $319$ discrete instances and
$134$ continuous instances.

>>>>

At the end of this process we had gathered more than eight thousand
instances. Three quarters of them contained discrete variables, while
the remainder contained only continuous variables. In more detail,
we gathered $\approx 1800$ Quadratic Binary Linear (\textit{QBL}) instances,
$\approx 2000$ Quadratic Continuous Quadratic (\textit{QCQ}) instances,
and $\approx 2500$ Quadratic General Quadratic (\textit{QGQ}) instances. We
also received $\approx 1000$ Convex General Convex (\textit{CGC}) instances. We
obtained relatively fewer Quadratic Binary Quadratic (\textit{QBQ}), Convex
Continuous Convex (\textit{CCC}) and Convex Mixed Convex (\textit{CMC}) instances,
($\approx 150$, $\approx 200$, and $\approx 200$ instances, respectively).
Finally, we found only $17$ Quadratic Mixed
Linear (\textit{QML}) instances. In the call for instances, no specific format
requirements were imposed for the submissions.

@@

During the development of the library, a discussion ensued about
the expected goals that we wished to achieve. The following four goals
were finally identified:
%
\begin{enumerate}
 \item to represent as far as possible all the different categories of QP
       problems;
 %
 \item to gather ``challenging'' instances, i.e., ones which can not be easily
       solved by  state-of-the-art solvers;
 %
 \item to include, for each of the categories, a set of well-diversified
       instances; and
 %
 \item to obtain a set of instances which is neither too small, so as to
       preserve statistical relevance, nor too large so as to being
       computationally manageable.
\end{enumerate}
%
To achieve such goals, we performed the following two filters, applied in
a cascade.
%
\begin{itemize}
 \item \emph{First Instances Filter.}\\
       The first filter was designed to drastically reduce the number of
       instances by eliminating the ``easy'' ones. An empirical measure
       for the hardness of an instance is the CPU time needed by a
       complete solver (cf.~\S\ref{sec:algo}) to solve it to
       global optimality. Accordingly, for each of the gathered instance we
       ran the complete solvers in GAMS, which number depends on the category
       of the instance under consideration, cf.~Table \ref{t:solvers}.
       We then filtered according to a first
       measure of computational difficulty, i.e., we discarded all instances
       that are solved by at least 30\% of the complete solvers within a time
       limit of 30 seconds.
 %
 \item \emph{Second Instances Filter.}\\
       The goal of the second filter was to eliminate ``similar'' instances.
       We carefully analyzed the instances one by one, and we clustered them
       according to their features; for each cluster we kept only a few
       representatives, e.g. by eliminating all but a few of those with very similar size and coming from the same donor. Finally, in order to only
       keep computationally challenging instances we ran a complete solver for \textit{QGQ} with a time limit of 120 seconds; all the
       instances which have been solved to proven optimality within this time limit
       were discarded.
\end{itemize}
%
In Table~\ref{tab:filters} we summarize the two filter steps, which
allowed us to identify the final set of $319$ discrete instances and
$134$ continuous instances.

### 2018-02-08 format.tex
consistent title case in section headers
problem types should be formatted in italics

\section{The file format}\label{sec:format}

@@

\item [{[2]}]
For problems of type \texttt{**N} or \texttt{**B}, these lines/sections
are omitted.
\item [{[3]}]
For problems of type \texttt{L**}, this section is omitted.
\item [{[4]}]
For problems of type \texttt{**N}, \texttt{**B} or \texttt{**L},
this section is omitted.
\item [{[5]}]
For problems of type \texttt{*C*}, \texttt{*B*} or \texttt{*I*},
this section is omitted. For problems of type \texttt{*I*}, binary variables
should be specified as integer variables with lower and upper bounds 0 and 1.
\item [{[6]}]
For problems of type \texttt{*B*}, this section is omitted.
%Bounds for binary variables must not be specified in this section.
\end{description}
Binary variables defined either implicitly via the type \texttt{*B*}
or explicitly in the variable type section will be assumed to
have lower and upper bounds 0 and 1, and this will override any
explicit bounds $l_d$, $u_d$, $l_i$, and $u_i$ set in the lower and upper
bound sections.
To fix a binary variable to 0 or 1, its variable type should be changed
to continuous or general integer and the corresponding lower and upper
bounds set accordingly in the lower and upper bound sections.

>>>>

\section{The File Format}\label{sec:format}

@@

\item [{[2]}]
For problems of type \textit{**N} or \textit{**B}, these lines/sections
are omitted.
\item [{[3]}]
For problems of type \textit{L**}, this section is omitted.
\item [{[4]}]
For problems of type \textit{**N}, \textit{**B} or \textit{**L},
this section is omitted.
\item [{[5]}]
For problems of type \textit{*C*}, \textit{*B*} or \textit{*I*},
this section is omitted. For problems of type \textit{*I*}, binary variables
should be specified as integer variables with lower and upper bounds 0 and 1.
\item [{[6]}]
For problems of type \textit{*B*}, this section is omitted.
%Bounds for binary variables must not be specified in this section.
\end{description}
Binary variables defined either implicitly via the type \textit{*B*}
or explicitly in the variable type section will be assumed to
have lower and upper bounds 0 and 1, and this will override any
explicit bounds $l_d$, $u_d$, $l_i$, and $u_i$ set in the lower and upper
bound sections.
To fix a binary variable to 0 or 1, its variable type should be changed
to continuous or general integer and the corresponding lower and upper
bounds set accordingly in the lower and upper bound sections.
